---
title: "Websurfing with R"
date: "July 2022"
author: "Tom Theile, Max-Planck-Institute for demographic research, theile@demogr.mpg.de"
output:
  pdf_document: default
---   
  
```{r setup, include=FALSE, warning=FALSE}
pagebreak <- function() {
  if(knitr::is_latex_output())
    return("\\newpage")
  else
    return('<div style="page-break-before: always;" />')
}

knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Reading a website with R

Requesting webpages can be done not only by using the webbrowser, but also by using any programming language. We will use R to do this. And we will use the R-package `rvest`, because it makes this very convenient.

Please google rvest, and you will get the installation-instructions:
  
```R
# The easiest way to get rvest is to install the whole tidyverse:
install.packages("tidyverse")

# Alternatively, install just rvest:
install.packages("rvest")
```

Now you can download any webpage with the simple command `read_html`:
  
```{r}
library(rvest)
simple_page <- read_html("https://user.demogr.mpg.de/theile/Files/edsd/simple.html")
print(paste(simple_page))
```

```
<!DOCTYPE html>
  <html>
  <body>
  
  <h1>Hello Barcelona!</h1>
  
  <p>This is some text.</p>
  
  <a href="https://www.example.com">This is a link</a>
  <a href="./simple2.html">This is also a link</a>
  </body>
  </html>
```


## What temperature is it right now?

# use selectorGadget to find the css selector:

```R
css_selector <-".current-w-temp"

page_weather <- read_html("https://kachelmannwetter.com/de/wetter/2844588-rostock")

temperature <- page_weather %>%
    html_nodes(css_selector) %>%   # This line selects all the html-elements with that css-selector
    html_text()   # This extracts only the Text of the selected html-elements

print(temperature)

```

